Numerical Stability of Detonations in White Dwarf Simulations

### 2019-02-06 papers/ignition/paper.tex
Minor modification to convergence language

\autoref{fig:self-heat-distance} shows our main results. The lowest resolution we consider,
256 km, is typical of the early simulations of white dwarf collisions, and demonstrates a
prompt ignition near the contact point. As the (uniform) resolution increases, the ignition
tends to occur earlier and nearer to the contact point. This trend is not physically meaningful:
all simulations with resolution worse than about 1 km represent the same prompt central ignition,
and as the resolution increases, there are grid points physically closer to the center that can ignite.
However, when the resolution is better than 1 km, the situation changes dramatically: the prompt
central ignition does not occur, but rather the ignition is delayed and occurs further from the contact
point. When we have finally \replaced{(perhaps) converged}{reached the point where the curves start to flatten},
the ignition occurs around 900 km from the contact point, about 1 second after contact (contrast to less than
0.05 seconds for the simulation with 1 km resolution). \added{Even at this resolution, it is not clear if
the simulation is converged. We were unable to perform higher resolution simulations to check convergence
due to the length of time that would be required.} This story contains two important lessons. First,
the required resolution for even a qualitatively converged simulation, less than 100 m, is out of reach
of current 3D supernova simulations. Second, the behavior for resolutions worse than 1 km qualitatively
appears to be converged, and one could perhaps be misled into thinking that there was no reason to
try higher resolutions, which is reason for caution in interpreting reacting hydrodynamics simulations.

>>>>

\autoref{fig:self-heat-distance} shows our main results. The lowest resolution we consider,
256 km, is typical of the early simulations of white dwarf collisions, and demonstrates a
prompt ignition near the contact point. As the (uniform) resolution increases, the ignition
tends to occur earlier and nearer to the contact point. This trend is not physically meaningful:
all simulations with resolution worse than about 1 km represent the same prompt central ignition,
and as the resolution increases, there are grid points physically closer to the center that can ignite.
However, when the resolution is better than 1 km, the situation changes dramatically: the prompt
central ignition does not occur, but rather the ignition is delayed and occurs further from the contact
point. When we have finally \replaced{(perhaps) converged}{reached the point where the curves start to flatten
and perhaps begin to converge}, 
the ignition occurs around 900 km from the contact point, about 1 second after contact (contrast to less than
0.05 seconds for the simulation with 1 km resolution). \added{Even at this resolution, it is not clear if
the simulation is converged. We were unable to perform higher resolution simulations to check convergence
due to the length of time that would be required.} This story contains two important lessons. First,
the required resolution for even a qualitatively converged simulation, less than 100 m, is out of reach
of current 3D supernova simulations. Second, the behavior for resolutions worse than 1 km qualitatively
appears to be converged, and one could perhaps be misled into thinking that there was no reason to
try higher resolutions, which is reason for caution in interpreting reacting hydrodynamics simulations.
